---
title: "DSRIP 1.4 Updates"
date: "2023-1-12"
output: 
  word_document:
      reference_docx: Waiver_report_styles.dotx
---

```{r, include = FALSE, echo=TRUE, fig.retina = 2}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE) 
source("/Users/tardis/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - Documents/DSRIP/DSRIP_1.3_quality_outcomes/analysis/settings.R")
source("/Users/tardis/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - Documents/DSRIP/DSRIP_1.4_pophealth_PPEs/analysis/analysis.R")

```
###### Figure II.14 Potentially Preventable Admissions
(PPA)
**Change y axis**

```{r,  fig.retina = 2}
ppa_sum_graph_w
```

`r ppa_res_weight_statement`

###### Figure II.15 Potentially Preventable Readmissions
(PPR)

```{r, fig.retina = 2}
ppr_sum_graph_w
```

`r ppr_res_weight_statement`

###### Figure II.16 Potentially Preventable Complications
(PPC)

```{r, fig.retina = 2}
ppc_sum_graph_w
```

`r ppc_res_weight_statement`

###### Figure II.17 Potentially Preventable ED Visits Actual-to-Expected Ratios
(PPV)

```{r, fig.retina = 2}
ppv_sum_graph_w
```

`r ppv_res_weight_statement`

# Appendix

###### Table B.25 Summary Statistics by Year: Potentially Preventable Admissions (PPA)
###### Summary Statistics by Year: 1.4.1 Potentially Preventable Admissions (PPA)

```{r}
 ppa_summary_stats 
```

`r ppa_summary_note`

###### Table B.26 Summary Statistics by Year: Potentially Preventable Readmissions (PPR)
###### Summary Statistics by Year: 1.4.2 Potentially Preventable Readmissions (PPR)

```{r}
ppr_summary_stats 
```

`r ppr_summary_note`

###### Table B.27 Summary Statistics by Year: Potentially Preventable Complications (PPC)
###### Summary Statistics by Year: 1.4.3 Potentially Preventable Complications (PPC)

```{r}
ppc_summary_stats 
```

`r ppc_summary_note`

###### Table B.28 Summary Statistics by Year: Potentially Preventable Emergency Department Visits (PPV)
###### Summary Statistics by Year: 1.4.4 Potentially Preventable Emergency Deparment visits (PPV)

```{r}
ppv_summary_stats
```

`r ppv_summary_note`
