---
title: "DSRIP Chapter Updates"
date: "2023-10-19"
output: 
  word_document:
      reference_docx: Waiver_report_styles.dotx

---

```{r, include = FALSE, echo=TRUE, fig.retina = 2}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE) 


source("/Users/tardis/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - Documents/DSRIP/DSRIP_1.3_quality_outcomes/analysis/settings.R")
source("/Users/tardis/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - Documents/DSRIP/DSRIP_1.1_survey/network/analysis/likertAnalysis.R", chdir = TRUE)
source("/Users/tardis/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - Documents/apm/analysis/oeq.R", chdir = TRUE)
source("/Users/tardis/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - Documents/DSRIP/DSRIP_1.1_survey/network/analysis/part_rates.r", chdir = TRUE)
source("/Users/tardis/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - Documents/DSRIP/DSRIP_1.1_survey/network/analysis/1_1_new.r", chdir = TRUE)
source("/Users/tardis/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - Documents/DSRIP/DSRIP_1.3_quality_outcomes/analysis/analysis.R")
source("/Users/tardis/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - Documents/DSRIP/DSRIP_1.4_pophealth_PPEs/analysis/analysis.R")



#Emily's path
#source("/Users/em/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - analysis (1)/settings.R")
#source("/Users/em/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - analysis/likertAnalysis.R", chdir = TRUE)
#source("/Users/em/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - analysis/part_rates.r", chdir = TRUE)
#source("/Users/em/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - analysis/1_1_new.r", chdir = TRUE)
#source("/Users/em/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - analysis (1)/analysis.R")
#source("/Users/em/Library/CloudStorage/OneDrive-SharedLibraries-TexasA&MUniversity/Team - waiver2_final - analysis (2)/analysis.R")

# Need to add oeq.R from APM to emiilys path
```

###### Table II.7 RHP participation rates by year

```{r}
part_rate

```

###### Measure 1.1.2 

(JSD, RS, DSA)

```{r,  fig.retina = 2}
dpm112jsdplot

dpm112trsplot

dpm112dsaplot

```

###### Figure II.3. Strength of network ties 
(Measure 1.1.3 - Density)

```{r,  fig.retina = 2}
dpm113denplot

```

###### Figure II.4. Average density of network ties
(JSD, RS, DSA)

```{r,  fig.retina = 2}
dpm114jsdplot

dpm114trsplot

dpm114dsaplot

```

###### Figure II.5. Average centralization of network ties

```{r,  fig.retina = 2}

dpm115jsdplot

dpm115trsplot

dpm115dsaplot

```

## Measure 1.1.6 

Attitude toward Collaboration

To understand the attitudes of DSRIP-participating providers toward DSRIP’s impact on collaborative relationships, specifically care coordination, providers were asked about the extent to which they agreed or disagreed with the following statements: 

•	DSRIP has increased the level of care coordination between different DSRIP providers.  

•	DSRIP has increased the level of care coordination between DSRIP and non-DSRIP providers.

###### DSRIP has increased the level of care coordination between different DSRIP providers.

```{r,  fig.retina = 2}
new_dc1$prim_vis_bar_tot
```

`r new_dc1$caption`

###### DSRIP has increased the level of care coordination between DSRIP and non-DSRIP providers.

```{r,  fig.retina = 2}
new_dc2$prim_vis_bar_tot
```

`r new_dc2$caption`

###### Table II.11 Health Information Exchanges used by Participating Providers


```{r, fig.retina = 2}

hie_other_oeq

```

`r caption_oeq_org_count`


###### Table II.12 Number and percentage of external organizations that provided DSRIP data

```{r,  fig.retina = 2}

out_data_oeq

```

`r caption_out`

###### Figure II.4 Overall Provider Achievement for A1-508 Rate of ED Visits for Diabetes

```{r, fig.retina = 2}
m1$prim_vis

```

###### Figure II.5 Population Impact: Change in Weighted Mean Rate: A1-508 Rate of ED Visits for Diabetes

```{r, fig.retina = 2}
ma1$wt_fig
```

`r ma1$caption_w`

###### Figure II.6 Overall Provider Achievement for A2-509 Rate of ED Visits for CHF, Angina, and Hypertension

```{r, fig.retina = 2}
m2$prim_vis
```

###### Figure II.7 Population Impact: Change in Weighted Mean Rate: A2-509 Rate of ED Visits for CHF, Angina, and Hypertension

```{r, fig.retina = 2}
ma2$wt_fig
```
`r ma2$caption_w`

###### Figure II.8 Overall Provider Achievement for H2-510 Rate for Behavioral Health and Substance Abuse

```{r, fig.retina = 2}
m3$prim_vis
```

###### Figure II.9 Population Impact: Change in Weighted Mean Rate: H2-510 Rate for Behavioral Health and Substance Abuse
(Comparison of Real and Target Weighted Mean Rates)

```{r, fig.retina = 2}
ma3$wt_fig
```

`r ma3$caption_w`
###### Figure II.10 Overall Provider Achievement for C1-502 Rate for the Adult Acute Composite Indicator

```{r, fig.retina = 2}
m4$prim_vis
```

###### Figure II.11 Population Impact: Change in Weighted Mean Rate: C1-502 Rate for the Adult Acute Composite Indicator
(Comparison of Real and Target Weighted Mean Rates)


```{r, fig.retina = 2}
ma4$wt_fig
```

`r ma4$caption_w`
###### Figure II.12 Overall Provider Achievement for D1-503 Rate for the Child Acute Composite Indicator

```{r, fig.retina = 2}
m5$prim_vis
```

###### Figure II.13 Population Impact: Change in Weighted Mean Rate: D1-503 Rate for the Child Acute Composite Indicator
(Comparison of Real and Target Weighted Mean Rates)

```{r, fig.retina = 2}
ma5$wt_fig
```

`r ma5$caption_w`
###### Figure II.14 Potentially Preventable Admissions
(PPA)
**Change y axis**

```{r,  fig.retina = 2}
ppa_sum_graph_w
```

`r ppa_res_weight_statement`

###### Figure II.15 Potentially Preventable Readmissions
(PPR)

```{r, fig.retina = 2}
ppr_sum_graph_w
```

`r ppr_res_weight_statement`

###### Figure II.16 Potentially Preventable Complications
(PPC)

```{r, fig.retina = 2}
ppc_sum_graph_w
```

`r ppc_res_weight_statement`

###### Figure II.17 Potentially Preventable ED Visits Actual-to-Expected Ratios
(PPV)

```{r, fig.retina = 2}
ppv_sum_graph_w
```

`r ppv_res_weight_statement`

# Appendix

###### Table B.20 Provider Measure Achievement: A1-508 Rate of ED Visits for Diabetes
###### Rate of Emergency Department Visits for Diabetes (A1-508: DSRIP Category C Measure 1.3.1)
###### Summary Statistics by Year and Measure Achievement: Rate of Emergency Department Visits for Diabetes


```{r}
m1$summary_stats
```

`r m1$note`

###### Figure B.6 Change in Unweighted Mean Rate: A1-508 Rate of ED Visits for Diabetes
(Comparison of Real and Target Mean Rates)

```{r, fig.retina = 2}
ma1$uw_fig
```

`r ma1$caption_u`

###### Table B.21 Provider Measure Achievement: A2-509 Rate of ED Visits for CHF, Angina, and Hypertension
###### Summary Statistics by Year and Measure Achievement: Rate of Emergency Department Visits for CHF, Angina, and Hypertension

```{r}
m2$summary_stats
```

`r m2$note`

###### Figure B.3 Change in Unweighted Mean Rate: A2-509 Rate of ED Visits for CHF, Angina, and Hypertension
(Comparison of Real and Target Mean Rates)

```{r, fig.retina = 2}
ma2$uw_fig
```

`r ma2$caption_u`

###### Table B.22 Provider Measure Achievement: H2-510 Rate of Emergency Department Visits for Behavioral Health and Substance Abuse
###### Summary Statistics by Year and Measure Achievement: Rate of Emergency Department Visits for Behavioral Health and Substance Abuse

```{r}
m3$summary_stats
```

`r m3$note`
###### Figure B.4 Change in Unweighted Mean Rate: H2-510 Rate of Emergency Department Visits for Behavioral Health and Substance Abuse
(Comparison of Real and Target Mean Rates)

```{r, fig.retina = 2}
ma3$uw_fig
```

`r ma3$caption_u`

###### Table B.23 Provider Measure Achievement: C1-502 PQI 91 Adult Acute Composite Indicator
###### Summary Statistics by Year and Measure Achievement: Prevention Quality Indicator 91: Adult Acute Composite Indicator

```{r}
m4$summary_stats
```

`r m4$note`

###### Figure B.5 Change in Unweighted Mean Rate: C1-502 PQI 91 Adult Acute Composite Indicator
(Comparison of Real and Target Mean Rates)

```{r, fig.retina = 2}
ma4$uw_fig
```

`r ma4$caption_u`

###### Table B.24 Provider Measure Achievement: D1-503 PDI 91 Child Acute Composite Indicator
###### Summary Statistics by Year and Measure Achievement: Pediatric Quality Indicator 91: Child Acute Composite Indicator

```{r}
m5$summary_stats
```

`r m5$note`

###### Figure B.6 Change in Unweighted Mean Rate: D1-503 PDI 91 Child Acute Composite Indicator
(Comparison of Real and Target Mean Rates)

```{r, fig.retina = 2}
ma5$uw_fig
```

`r ma5$caption_u`

###### Table B.25 Summary Statistics by Year: Potentially Preventable Admissions (PPA)
###### Summary Statistics by Year: 1.4.1 Potentially Preventable Admissions (PPA)

```{r}
 ppa_summary_stats 
```

`r ppa_summary_note`

###### Table B.26 Summary Statistics by Year: Potentially Preventable Readmissions (PPR)
###### Summary Statistics by Year: 1.4.2 Potentially Preventable Readmissions (PPR)

```{r}
ppr_summary_stats 
```

`r ppr_summary_note`

###### Table B.27 Summary Statistics by Year: Potentially Preventable Complications (PPC)
###### Summary Statistics by Year: 1.4.3 Potentially Preventable Complications (PPC)

```{r}
ppc_summary_stats 
```

`r ppc_summary_note`

###### Table B.28 Summary Statistics by Year: Potentially Preventable Emergency Department Visits (PPV)
###### Summary Statistics by Year: 1.4.4 Potentially Preventable Emergency Deparment visits (PPV)

```{r}
ppv_summary_stats
```

`r ppv_summary_note`
